Low prevalence of \emph{a priori} power analyses in motor behavior research

### 2022-07-13 docs/preprint/preprint.Rmd
update: fix behaviour spelling in github links

## Open Science Practices
\noindent The preregistration, data, and scripts can be accessed using either of the following links: https://osf.io/wsdpv/ or https://github.com/cartermaclab/proj_power-motor-behavior.

>>>>

## Open Science Practices
\noindent The preregistration, data, and scripts can be accessed using either of the following links: https://osf.io/wsdpv/ or https://github.com/cartermaclab/proj_power-motor-behaviour.
